\starttext


Research in any field implies a step ahead in exploration of unknowns. Research methodology tells the procedure used for the research. It is a 
combination of two words research and methodology. Research is used to describe a collection of information about a particular subject. Methodology 
means the science of dealing with principles or procedure in research and study. Research methodology means an abstraction or constitution of research. 
It is a way to systematically solve the research problem [39]. This chapter has been divided into nine sections. Section 3.1 problem statement defines 
research problem, Section 3.2 describes objectives of the present study, Section 3.3 describes research approach and its types and discuss method that 
are used in the present study, Section 3.4 describes data collection and analysis, Section 3.5 describes the Technique used, Section 3.6 describes User 
Profile-Understanding how user works, Section 3.7 Scope of Study, Section 3.8 Limitation of Study describes the limits of present study and Section 3.9 
is about Chapter Scheme.


\section{Problem Statement}

Many problems encounter while predicting the behavior of user. Present problem is entitled as “DESIGNING OF AN ALGORITHM FOR GRAPHICAL PASSWORD 
AUTHENTICATION SYSTEM”. The present study is used to find behavior of user by using clustering approach. The present study is used to find similar 
groups of records in very large datasets so that clusters can be formed from the data. All the similar data are placed in one cluster and entirely 
different data are placed in different clus


\section{Objective of Research Work}

\definesymbol[5][$\clubsuit$]
\startitemize[5,packed]


\item To predict the behavior of web user.
\item To detect the fraud and threat in the web data.
\item To ensure privacy among web data.
\item To optimize the performance of web services using mining of web data.


\stopitemize

\section{Research Approach}

Research means search for knowledge. Research is the systematic investigation into and study of materials, sources etc. in order to establish facts and 
reach new conclusions. According to the advanced learner dictionary of current English, the meaning of research is a careful investigation or enquiry 
especially through search for new facts in any branch knowledge. The main purpose of research is to discover answer to questions through the 
application of scientific procedures. The main aim of research work is to find out the truth which is hidden and which has not been discovered yet 
[39]. Different approach is taken to conduct a research such as inductive research and deductive methods, inferential, case study, experimental, 
analytical and of simulation type. Deductive research starts with some predefined theories and concepts and on the basis of these concepts they 
generate hypothesis that are tested subsequently. Inductive research starts with real world data and categories and theories emerges from this input. 
The objective of inferential approach is to form a database from which the population of the characteristics can be inferred [39]. The applied research 
is discovering, interpreting and the development of methods and systems for the advancement of human knowledge on a wide variety of scientific matters 
of the world and the universe [39]. The Research process step order may vary depending on the subject matter and researcher, the steps followed during 
formal research either it is basic or applied are choosing the research problem, review of related literature, collection of data, interpretation of 
data and preparing the research report [39]. The basic research is geared toward advancing the knowledge about human behavior with little concern for 
any immediate practical benefits that might result. The goal of the research process is to produce new knowledge which takes three main forms. First is 
exploratory research which structures and identifies new problem. Second is constructive research which develops solution to a problem. Third is 
empirical research which tests the feasibility of solution using empirical evidences [39]. The research method used is to study a real time object 
oriented asynchronous production system is the constructive research method. It is also important to choose a research method which is within the 
limits of what the researcher can do. Time, money, feasibility, ethics and availability to measure the phenomenon correctly are examples of issues 
constraining the research [39]. Experimental research is a systematic and scientific approach to manipulate and control testing to understand casual 
process. It is true experimental research. Experimental approach has a greater control over the research environment. In this type of research some 
variables are manipulated to observe their effect on other variables. Simulation approach deals with construction of artificial environment within 
which relevant information can be gathered. This allows an observation of dynamic behavior of a system under control condition [39].  Analytical 
research is a type of research in which the collected data is reviewed to make sine conclusion. Many type of analytical research are known till date 
such as literature research, public opinion, scientific trials and meta-analysis. The Literature research uses books or stories as a data source. The 
public opinion type research collects the data by knowing the interests and opinion of general public. For scientific trials, the data is gathered by 
actually implementing some experiment in the labs. For conducting this research the scientist may design the by experiment and finally may get the 
result by conducting that experiment. In meta-analysis the already analyzed behavior is behaved as a next set of data and next analysis is performed by 
considering the value of this new set. A number of statistical methods are finally used to draw conclusion from the data [39].


\subsection{Research Method used in present study}


In the present research analysis and experiments are conducted on varying number of data. In this study the prediction of the behavior of user that 
surf the web is presented, which is based on how many time a user can use any site, how much time the user uses the site. The IP address is used as a 
parameter for clustering. Based on the IP address the clustering is done. Varying number of cluster are formed and then by using this the behavior of 
the user is predicted. In this dissertation “Analysis of Web Data using Clustering Approach” a simulator is used to analyze prediction of the behavior 
of user. This method gives a faster approach to analyze the behavior of user and hence ensure privacy among web data.



\stoptext
